Communication in Agile Inter-team Development

### 2019-02-03 Draft/Parts/Main.tex

System design and architecture acts as a common framework for not only teams but also for the communication between all the product owners.
The system design acts as a “deadlock breaker in decisions” \cite{architecureRole_article} for situations where teams disagree on a particular design path, and ensures that components will be constructed so they can be integrated into the whole.
%non specification fix
A second approach addresses this issue from an organizational standpoint by defining a "system owner" role \cite{kniberg12}.
This role is more casual than an architect role, and focuses on defining a "go-to" person who can maintain a long term stewardship over a sub-system.

>>>>

System design or architecture acts as a common vision for not only the teams but also for the communication between all the product owners and thus is the theme or topic for most of the inter-team communication that happens in a multi-team agile environment.
Being such a frequent piece of discussion, it needs to be as formal and as clearly defined as possible as it is the system design that acts as a “deadlock breaker in decisions” \cite{architecureRole_article} for situations where teams disagree on a particular design path.
System design and architecture acts as a common framework for not only teams but also for the communication between all the product owners and thus is the theme or topic for most of the inter-team communication that happens in a multi-team agile environment.
Being such a frequent piece of discussion, it needs to be as formal and as clearly defined as possible as it is the system design that acts as a “deadlock breaker in decisions” \cite{architecureRole_article} for situations where teams disagree on a particular design path, and ensures that components will be constructed so they can be integrated into the whole.
%non specification fix
A second approach addresses this issue from an organizational standpoint by defining a "system owner" role \cite{kniberg12}.
This role is more casual than an architect role, and focuses on defining a "go-to" person who can maintain a long term stewardship over a sub-system.
